Revenue Maximization for Buyers with Costly Participation

### 2025-03-19 paper/paper.tex
Address privacy of participation costs

\begin{section}{Introduction}
 Commonly in mechanism design problems auctions are modeled as free to participate in.
 However, this does not necessarily reflect how in reality mechanism exist.
 For example, consider the case that for moving to a new city one wants to buy a house that is sold in an auction.
 To participate there, one at least need to be present and therefore might pay for travel, accommodation and also incur some loss opportunity for not being elsewhere.
 All those costs we refer to as participation costs of an auction for this buyer.
 As buyers might not be convinced to share those costs publically beforehand, e.g. since it might be sensitive information, we are studying the problem of private participation costs.

@@

 To model the private participation costs, each buyer now additionally has participation costs $c_i \in \RR$ \cite{primary}.
 The mechanism $\mathcal{M}' = (x', p')$ will respect that participation costs as well.
 A buyer's utility is reduced by her participation cost if she participates.

 \begin{align*}
     u_i^{\mathcal{M}'} = \begin{cases}
                              v_i x_i(v_i, c_i) - p_i(v_i, c_i) - c_i & \text{if $i$ participates} \\
                              0                                       & \text{otherwise}
                          \end{cases}
 \end{align*}
 We will call a buyer's type the tuple of valuation and participation cost $t_i = (v_i, c_i)$.
 We study the setting where each buyer's type is drawn from a distribution $\bar{F_i}$.
\end{section}

>>>>

\begin{section}{Introduction}
 Commonly in mechanism design problems auctions are modeled as free to participate in.
 However, this does not necessarily reflect how in reality mechanism exist.
 For example, consider the case that for moving to a new city one wants to buy a house that is sold in an auction.
 To participate there, one at least need to be present and therefore might pay for travel, accommodation and also incur some loss opportunity for not being elsewhere.
 All those costs we refer to as participation costs of an auction for this buyer.
 As buyers might not be convinced to share those costs publically beforehand, e.g. since it might be sensitive information, we are studying the problem of \textit{private participation costs}.

@@

 To model the \textit{private} participation costs, each buyer now additionally has participation costs $c_i \in \RR$ \cite{primary}.
 The mechanism $\mathcal{M}' = (x', p')$ will respect that participation costs as well.
 A buyer's utility is reduced by her participation cost if she participates.

 \begin{align*}
     u_i^{\mathcal{M}'} = \begin{cases}
                              v_i x_i(v_i, c_i) - p_i(v_i, c_i) - c_i & \text{if $i$ participates} \\
                              0                                       & \text{otherwise}
                          \end{cases}
 \end{align*}
 We will call a buyer's type the tuple of valuation and participation cost $t_i = (v_i, c_i)$.
 We study the setting where each buyer's type is drawn from a distribution $\bar{F_i}$.

 Note that since both the valuation and the participation costs are private, this model also allows for correlation between the two, therefore is more general than using public participation costs.  
\end{section}
